Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-10-17 parts/intro.tex
edits

All this motivates the use of strong gravitational lensing over galaxy
scales to study the mutual dynamics of dark matter, gas and stars.
Several studies in recent years have done so \citep[see,
  e.g.,][]{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their mass
distribution.  Recent searches through the CFHT Lens Survey
\citep[CFHTLS,][]{2012MNRAS.427..146H} using arc-finders
\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
by either machine learning methods 
\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} or visual
inspection by citizen-science volunteers through the \SW project 
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree, so one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from ground-based surveys such as LSST in the optical window
and SKA in radio, to space-based missions such as Euclid and WFIRST 
\citep{2010MNRAS.405.2579O,2015ApJ...811...20C}.

@@

We emphasize that the interpretation of the results presented here is
tentative, because the systems are lens candidates at this stage, not
secure lenses.  Moreover the candidate-lens redshifts have large
uncertainties, while the candidate-source redshifts can only be
guessed at present.  Nevertheless it is interesting to explore the
trends observed with the already available data, based on some 300 models
created by 8 volunteers for 58 candidate lenses found in the 150\sqdeg
CFHTLS.  The availability of the recently published year 1 result of the
Dark Energy Survey \citep{2017arXiv170801531D},
which covered 1800\sqdeg, suggests that
these numbers have the possibility to grow by at least an order of
magnitude within a very short time period.
Moreover, ongoing work by Denzel et al. (in prep) will provide much more
strict bounds on the uncertainties presented in this work.

>>>>

All this motivates the use of strong gravitational lensing over galaxy
scales to study the mutual dynamics of dark matter, gas and stars.
Several studies in recent years have done so \citep[see,
  e.g.,][]{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their mass
distribution.  Recent searches through the CFHT Lens Survey
\citep[CFHTLS,][]{2012MNRAS.427..146H} using arc-finders
\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
by either machine learning methods
\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} or visual
inspection by citizen-science volunteers through the \SW project
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree, so one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from ground-based surveys such as LSST in the optical window
and SKA in radio, to space-based missions such as Euclid and WFIRST
\citep{2010MNRAS.405.2579O,2015ApJ...811...20C}.  The availability of
the recently published year~1 result of the Dark Energy Survey
\citep{2017arXiv170801531D}, which covered 1800\sqdeg, suggests that
the number of lenses could grow by at least an order of magnitude
within a very short time period.
% Moreover, ongoing work by Denzel et al. (in prep) will provide much more
% strict bounds on the uncertainties presented in this work.

@@

We emphasize that the interpretation of the results presented here is
tentative, because the systems are lens candidates at this stage, not
secure lenses.  Moreover the candidate-lens redshifts have large
uncertainties, while the candidate-source redshifts can only be
guessed at present.  Nevertheless it is interesting to explore the
trends observed with the already available data, based on some 300 models
created by 8 volunteers for 58 candidate lenses found in the 150\sqdeg
CFHTLS.
